Arms Transfers and Frozen Conflict Dynamics

### 2024-04-16 paper.qmd
Notes

files <- list.files("posteriors", "csv$", full.names = T)
stopifnot(length(files) > 0)

@@

Shortcomings:
- Frozen conflict measure does not account for the ability of actors
  to re-escalate a conflict --- no distinction between a weakened
  insurgency versus a de facto separatist state
- Excluded low intensity conflicts

>>>>

files <- list.files("posteriors", "^output_\\d.csv$", full.names = T)
stopifnot(length(files) > 0)

@@

Shortcomings:
- Frozen conflict measure does not account for the ability of actors
  to re-escalate a conflict --- no distinction between a weakened
  insurgency versus a de facto separatist state (DOES NOT MEASURE REBEL CAPACITY)
- Excluded low intensity conflicts
